\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\singlespacing

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\renewcommand\thesection{\Alph{section}}



\begin{document}


\input{./title.tex}





\section{Project Description}\label{project-description}

\subsection{Background}\label{background}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Where to start?
\item
  The Psychology of Decision Making
\item
  Wearable Technology

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Advantages
  \item
    Disadvantages
  \item
    Synthesis:
  \end{itemize}
\item
  How Technology Could Aid Decision Making?
\end{itemize}

A graph of workload v.s. time?

(Identify this as a problem to be solved / innovation)

\subsection{This Project}\label{this-project}

A synopsis for the background / purpose and methods --\textgreater{}
know what's going on.

\subsection{Methods}\label{methods}

Break down into tasks:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  What are the senior design people doing?
\item
  Steps:

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Experiments? / equipment (the watch - ish gardget?)
  \item
    Coding?
  \item
    Established psychology methods?
  \item
    Lit. review?
  \end{itemize}
\item
  Explain why this project is super awesome and \textbf{feasible}
\end{itemize}

A summative flow chart-ish figure?

\subsubsection{Timeline}\label{timeline}

June, July, August

\subsection{Anticipated Outcome}\label{anticipated-outcome}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Making people's lives better
\item
  Measurable?
\item
  Writing?
\item
  Conference?
\end{itemize}

Need to mention why I qualify for the job??

\section{Research Environment}\label{research-environment}

I will work closely with Professor Peck throughout the research period.
We will arrange \ldots{} {[}frequency{]}{[}Availability{]}

Where: in comp. labs

\end{document}